---
title: "P8122-Homework3-yz4184"
author: "Yunlin Zhou"
date: '2022-10-09'
output: word_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
# data import
set.seed(124)
n <- 16
p_C <- 1/5
C <- rbinom(n,1,p_C)
theta0 <- 1/2
theta1 <- -1/5
p_A <- theta0+theta1*C
A <- rbinom(n,1,p_A)
beta0 <- 110
beta1 <- 20
beta2 <- 5
sigma_Y <- 1
mu_Y <- beta0+beta1*C+beta2*A
Y <- rnorm(n,mu_Y, sigma_Y)
```

# Question a

p: The baseline covariate C (obesity) follows Bernoulli distribution. p is the probability of C taking 1 (with obesity).

theta0: The original probability of assigning the units to treatment group (light) if there were no baseline covariate C.

theta1: The probability of assigning the units with obesity to treatment group (light) is 1/5 times lower than the units without obesity on average.

beta0: The mean of baseline glucose without baseline covariate C and treatment assignment A.

beta1: The change in the mean of glucose between the mice with obesity and the mice without obesity, conditionally on treatment assignment A. 

beta2: The change in the mean of glucose between the treatment group (light) and the control group (dark), conditionally on baseline covariate C (obesity). 


# Question d

```{r}
mice_df = cbind(Y, A, C)%>%
  as.data.frame()
```


```{r}
mice_df$interv <- -1 

interv0 <- mice_df
interv0$interv <- 0
interv0$A <- 0
interv0$Y<- NA

interv1 <- mice_df 
interv1$interv <- 1
interv1$A <- 1
interv1$Y<- NA

onesample <- rbind(mice_df, interv0, interv1) 
```


```{r}
std <- glm(
  Y ~ A + C,
  data = onesample
)
onesample$predicted_meanY <- predict(std, onesample)
```


```{r}
mean_0_c =mean(onesample[which(onesample$interv == 0), ]$predicted_meanY)


mean_1_c = mean(onesample[which(onesample$interv == 1),]$predicted_meanY)
```


```{r}
mean_1_c - mean_0_c
```


# Question e

```{r}
df = onesample %>%
  filter(interv == -1)

mean_1 = mean(df[which(df$A == 1), ]$predicted_meanY)
mean_0 = mean(df[which(df$A == 0), ]$predicted_meanY)
mean_1 - mean_0
```


## another try

```{r}
mice_df_2 = cbind(mu_Y, A, C)%>%
  as.data.frame()
```


```{r}
mean_0_y =mean(mice_df_2[which(mice_df_2$A == 0), ]$mu_Y)


mean_1_y = mean(mice_df_2[which(mice_df_2$A == 1),]$mu_Y)
```


```{r}
mean_1_y- mean_0_y
```
```




































































